Pilot study APEROL: questionnaire data

### 2021-01-22 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd

# demographics, grouped by group (N, gender, meanage, max, min age)
raw.data %>%
  filter(what == "head") %>%
  group_by(group) %>%
  summarise(N=n(),
            "male" = sum(gender),
            "mean age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age)
            ) %>% 
  knitr::kable(digits = 2)

@@

# to create error bars, we need to summarize the data in a separate data frame
phb.plot.sd <- phb.data %>%
  filter (perspective == "teacher") %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

# and here comes the long plot
phb.plot<-ggplot(data = phb.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid()+
  labs(data = phb.data, y = "value", x = NULL,
       title="presence: posture and gaze" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
phb.plot

>>>>

# demographics, grouped by group (N, gender, meanage, max, min age)
raw.data %>%
  filter(what == "head") %>%
  group_by(group) %>%
  summarise(N=n(),
            "male" = sum(gender),
            "mean age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age),
            "experience" = round(mean(experience), 2)
            ) %>% 
  knitr::kable(digits = 2)

@@

# to create error bars, we need to summarize the data in a separate data frame
phb.plot.sd <- phb.data %>%
  group_by(group, item.wordings, .drop=TRUE) %>%
  summarise(perspective, mean = mean(value), n = n(), sd = sd(value), se = sd/sqrt(n), )

names(phb.plot.sd)

# and here comes the long plot
phb.plot<-ggplot(data = phb.plot.sd,
                  aes(x = item.wordings, y = mean,
                      group = group, colour = group)) +
  geom_line()+
  geom_pointrange(position = position_dodge(0.1), aes(ymin = mean-se, ymax = mean+se))+
  theme_light() +
  ylim(1,4)+
  facet_grid(~perspective)+
  labs(data = phb.data, y = "value", x = NULL,
       title="presence: posture and gaze" ,
       subtitle=NULL)+
  theme(legend.position="bottom",
        panel.spacing.x = ,
        plot.title = element_text(hjust = 0.5))+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 55))+
  coord_flip()
phb.plot
